\addcontentsline{toc}{chapter}{Bibliography}
\begin{thebibliography}{9}

\bibitem{gh}
W. Goddard, M. A. Henning,
\textit{Thoroughly distributed colorings},
arXiv preprint arXiv:1609.09684.

\bibitem{outerplanar}
Z. L. Nagy,
\textit{Coupon-coloring and total domination in Hamiltonian planar triangulations},
arXiv preprint arXiv:1708.01725.

\bibitem{hypergraph}
Z. Dvorák, D. Král,
\textit{On planar mixed hypergraphs},
Journal of Combinatorics 8 (1), 35-35.

\bibitem{barnette}
D. W. Barnette,
\textit{Conjecture 5},
Recent progress in combinatorics (ed. W. T. Tutte), Academic Press, New York (1969) 343.


\bibitem{zelinka}
B. Zelinka,
\textit{Total domatic number and degree of vertices of a graph},
Mathematica Slovaca, Vol. 39 (1989), No. 1, 7--11.

\bibitem{np-complete}
P. Heggernes, J. A. Telle,
\textit{Partitioning graphs into generalized dominating sets},
Nordic Journal of Computing. 5 (2), 128-142.

\bibitem{regular}
H. Aram, S. M. Sheikholeslami, L. Volkmann,
\textit{On the total domatic number of regular graphs},
Transactions on Combinatorics 1, 45-51.

\bibitem{horton}
J. A. Bondy, U. S. R. Murty,
\textit{Graph theory with applications},
New York: North Holland, pp. 61 and 242, 1976.

\bibitem{tait}
P. G. Tait,
\textit{Listing's topologie},
Philosophical Magazine, 5th Series, 17: 30–46. Reprinted in Scientific Papers, Vol. II, pp. 85–98.

\bibitem{tutte}
W. T. Tutte,
\textit{On Hamiltonian circuits},
Journal of the London Mathematical Society, 21 (2): 98–101.

\bibitem{kelmans}
A. K. Kelmans,
\textit{Constructions of cubic bipartite 3-connected graphs without Hamiltonian cycles},
Selected Topics in Discrete Mathematics: Proceedings of the Moscow Discrete Mathematics Seminar 1972–1990,
American Mathematical Society Translations, Series 2, 158, pp. 127–140.

\bibitem{florek}
J. Florek,
\textit{On Barnette's conjecture},
Discrete Mathematics, 310 (10-11): 1531–1535.

\bibitem{ham1}
H. Whitney,
\textit{A theorem on graphs},
Annals of Mathematics 32 (1931), 378-3 90.

\bibitem{ham5}
G. Helden,
\textit{Hamiltonicity of maximal planar graphs and planar triangulations},
These de doctorat, RWTH Aachen University.


\bibitem{algorithm}
D.Avis,
\textit{Generating rooted triangulations without repetitions},
Algorithmica (1996) 16: 618-632

\end{thebibliography}
