In this chapter we will examine the so-called total domatic number of graphs.

Let $G = (V, E)$ be a graph without isolated vertices.

\begin{definition}
  $S \subseteq V$ is a total dominating set if every vertex has a neighbor in
  $S$. The total domatic number of $G$ is the maximum number of disjoint total
  dominating sets.
\end{definition}

Sometimes it is more convenient to look at total dominating sets as color classes.

\begin{definition}
  A coloring of the vertices is called a $k$-coupon coloring if every vertex
  has a neighbor from each color class. The coupon coloring number of $G$ is
  the maximum $k$ for which a $k$-coupon coloring exists. The coupon coloring
  number is denoted by $\chi_c(G)$.
\end{definition}

\begin{remark}
  We refer as proper colorings to colorings in the usual sense. I.e. colorings of
  the vertices such that for every vertex $v$, none of the neighbors of $v$ has the
  same color as $v$.
\end{remark}

\section{Complexity}

It turns out that determining the total domatic number (or equivalently the
coupon coloring number) of a graph is rather hard. Heggernes and Telle (TODO:REF) showed that
even determining whether the total
domatic number of a graph is at least $2$ is NP-complete. We prove this by showing
that a variant of 3SAT is reducible to this question in polynomial time.

\begin{definition}
  An instance of the not-all-equal 3-satisfiability (NAE-3SAT) problem consists of
  a set $C$ of clauses on a finite set $X$ of Boolean variables, where each clause
  contains three literals. The question is whether there is a truth assignment for
  $X$ that satisfies all the clauses in $C$ such that each clause contains a false
  literal.
\end{definition}

\begin{thm}
  NAE-3SAT is NP-complete.
\end{thm}
\begin{proof}
  It can be checked in polynomial time whether a given truth assignment meets the
  requirement, so NAE-3SAT is in NP.

  To prove NP completeness, we show first a reduction from 3SAT to NAE-4SAT.
  Let $C$ be the set of clauses and $X$ be the set of variables in an instance of
  3SAT. Let $X' = X \cup y$, and $C' = \{(x_1 \vee x_2 \vee x_3 \vee y)\ |\
  (x_1 \vee x_2 \vee x_3) \in C\}$. We claim that the NAE-4SAT problem defined
  by $(C', X')$ is satisfiable if and only if the 3SAT problem defined by $(C, X)$
  is satisfiable. If the 3SAT formula is satisfied by a truth assignment then
  the same assignment with assigning the value false to $y$ satisfies the NAE-4SAT
  problem. Now suppose a truth assignment satisfies the NAE-4SAT problem. If $y$
  has value false, then the same assignment of $X$ satisfies the 3SAT problem.
  If $y$ has value true, then changing every truth value in $X$ to its opposite
  gives a truth assignment satisfying the 3SAT formula.

  Finally, the reduction from NAE-4SAT to NAE-3SAT is by adding clauses
  $(x_1 \vee x_2 \vee z)$ and $(\bar{z} \vee x_3 \vee y)$ instead of each clause
  $(x_1 \vee x_2 \vee x_3 \vee y) \in C'$.
\end{proof}

\begin{thm}
  It is NP-complete to decide whether the total domatic number of
  a graph is at least $2$.
\end{thm}

\begin{proof}
  Given a partition of the vertices into $2$ sets, it can be checked in polynomial
  time whether these sets are total dominating sets. So the problem is a member
  of NP.

  For proving NP-completeness, we will show that NAE-3SAT is reducible to this problem
  in polynomial time. Let $C$ be the set of clauses and $X$ be the set of variables
  in an instance of NAE-3SAT. We can assume that every variable $x$ appears in at least
  one clause. Otherwise we add a new clause containing $x$ and $\bar{x}$ to
  the formula. Now we construct the corresponding graph $G$. For each variable $x$,
  introduce $3$ vertices $x_1, x_2, x_3$, and $2$ edges $x_1x_2, x_2x_3$. For each
  clause $c$, introduce a vertex $c$. If $x$ is a literal in $c$, then add the edge
  $cx_1$ to the graph. If $\bar{x}$ is a literal in $c$, then add the edge $cx_3$.

  Suppose $G$ has a partition into $2$ disjoint total dominating sets: $T$ and $F$.
  Assign the value true for each variable $x$ with $x_1 \in T$ and assign the value
  false otherwise. For any variable $x$, $x_1$ and $x_3$ are the only neighbors
  of $x_2$, so $x_1$ and $x_3$ must be in different sets of the partition. If $c$
  is a vertex corresponding to a clause, then it must have neighbors both in $T$
  and $F$, and so the literals in $c$ cannot be all true nor false.

  Suppose now that the variables have a truth assignment such that each clause
  contains both true and false literals. Define $T$ and $F$ as follows. Put all
  the vertices corresponding to clauses into $T$. For each variable $x$ put $x_2$
  into $F$. Furthermore, if true was assigned to $x$, then put $x_1$ into $T$, $x_3$
  into $F$, and conversely otherwise.
\end{proof}

Let us note that the constructed graph in the proof is always a bipartite
graph.

\begin{cor}
  It is NP-complete to decide whether the total domatic number of
  a bipartite graph is at least $2$.
\end{cor}

\section{Degree restrictions}

A natural question is whether graphs with an appropriately big minimum degree
always have a total domatic number of at least $2$. Zelinka (TODO:REF) showed
that this is not the case.

\begin{thm}
  For every $\delta \in \mathbb{Z}^+$ there exists a graph without $2$
  disjoint total dominating sets with minimum degree $\delta$.
\end{thm}
\begin{proof}
  We define a bipartite graph $G = (U, V ; E)$ for arbitrary $\delta$ as follows.
  Let $U$ be a set of cardinality $2\delta - 1$, and $V$ be the set of all subsets of
  $U$ consisting of $\delta$ elements. For all $ u \in U, v \in V$ vertices $uv \in E$
  if and only if $v$ contains $u$. Clearly, each vertex of $U$ has at least $\delta$
  neighbors, and each vertex of $V$ has exactly $\delta$ neighbors. Suppose that
  there exists a $2$-coupon coloring. Then there exists a monochromatic $U_0 \in U$
  containing $\delta$ vertices. Thus, there exists a $v \in V$ corresponding to $U_0$.
  That is a contradiction, since the neighborhood of $v$ is $U_0$, and that is monochromatic.
\end{proof}

A natural next question might arise. The graph constructed above has a large number
of vertices compared to the minimum degree. The other extreme is the case of
complete graphs, where the minimum degree $\delta$ is $n - 1$. This is not an interesting case:
if $n \ge 4$, then every subset $U$ of the vertices is a total dominating set, if $|U| \ge 2$.
We show a less strict but sufficient condition for the existence of $2$ disjoint dominating sets:
a lower bound for the minimum degree defined by the order of the graph.
The next theorem is also from Zelinka (TODO:REF). We show here an easier proof than
the original.

\begin{claim}
  Let $G = (V,E)$ be a graph of order $n$ with minimum degree $\delta$. Then every subset
  of $V$ with at least $n - \delta + 1$ vertices is a total dominating set.
\end{claim}
\begin{proof}
  Let $S \subseteq V$ be a set of cardinality at least $n - \delta + 1$ and $v \in V$ be
  an arbitrary vertex. $v$ has at least $\delta$ neighbors, and $|(V - v) \cap S| \ge
  n - \delta$, so there must exist a vertex $u \in S$ adjacent to $v$.
\end{proof}

\begin{cor}
  Let $G = (V,E)$ be a graph of order $n$ with minimum degree $\delta$. If $\delta \ge 1 + n/2$,
  then there exist $2$ disjoint dominating sets in $G$.
\end{cor}
\begin{proof}
  If $\delta \ge 1 + n/2$, then $2(n - \delta + 1) \le n$, and therefore the total
  domatic number of $G$ is at least $2$.
\end{proof}

\begin{remark}
  Aram, Sheikholeslami and Volkmann (TODO:REF) proved a lower bound for the total
  domatic number in terms of the order, the minimal and the maximal degree of the
  graph. Using this lower bound they proved that the domatic number of an $r$-regular graph
  is at least $r/3ln(r)$. By an easy calculation follows from this theorem that
  if a graph is $r$-regulat with $r \ge 5$, then the total domatic number is at least
  $2$.
\end{remark}
