\section{Complexity results}
TODO

\section{Connection to the Goddard-Henning conjecture}

Statement \ref{s:2-factor} gives a satisfactory condition for the conjecture of
Goddard and Henning. With the help of this, we can show another proof for \ref{c:odd}.

\begin{thm}\label{thm:odd}
  Let $G$ be a a simple triangulated graph of order at least $4$. If all the
  vertices of $G$ have an odd degree, then there exists a coupon coloring with $2$ colors.
\end{thm}
\begin{proof}
  Let $G^*$ be the dual of $G$. Take a $4$-coloring $c_{face}$ of the faces of
  $G$ with the colors $\{ 1, 2, 3, 4 \}$, such that faces with common edges belong to
  different color classes. Now we define a coloring on the edges. For an edge $e$,
  let $f_e^1$ and $f_e^2$ denote the faces containing $e$. Define the coloring as follows.
  \[
    c_{edge}(e) =
    \begin{cases}
      1, & \text{if}\ (c_{face}(f_e^1) = 1 \ \text{and}\ c_{face}(f_e^2) = 2) \ \text{or}\
        (c_{face}(f_e^1) = 3 \ \text{and}\ c_{face}(f_e^2) = 4)\\
      2, & \text{if}\ (c_{face}(f_e^1) = 2 \ \text{and}\ c_{face}(f_e^2) = 3) \ \text{or}\
        (c_{face}(f_e^1) = 1 \ \text{and}\ c_{face}(f_e^2) = 4)\\
      3, & \text{if}\ (c_{face}(f_e^1) = 1 \ \text{and}\ c_{face}(f_e^2) = 3) \ \text{or}\
        (c_{face}(f_e^1) = 2 \ \text{and}\ c_{face}(f_e^2) = 4)
    \end{cases}
  \]
  This way $c_{edge}$ is a coloring without edges of the same color having a common
  endpoint. Thus the union of any two color classes defines a $2$-factor. Let $H^*$
  be such a $2$-factor. From the degree restriction on $G$ follows that every face
  in $G^*$ has an odd number of edges. Hence $H^*$ does not contain any faces. With this,
  we have proven that Statement \ref{s:2-factor} holds and then by Claim \ref{c:2-factor}
  $G$ has a $2$-coupon coloring.
\end{proof}
